\pdfbookmark{首页}{TitlePage}
\thispagestyle{empty}

\vspace*{\stretch{1}}
\noindent
\begin{minipage}{\textwidth}
  \raggedleft{\huge \bfseries Writing GNU Emacs Extensions}
  \noindent\rule[-1ex]{\textwidth}{5pt}\\[2.5ex]
  \hfill\emph{\Large 中文版}
\end{minipage}

\vspace{\stretch{1}}
\noindent\rlap{%
  \begin{minipage}{\textwidth}
  \linespread{2}\selectfont\raggedleft
  {\bfseries 英文作者：} Bob Glickstein \\
  {\bfseries 英文版本：} April 1997: First Edition. \\
  {\bfseries 中文翻译：} \href{https://github.com/slegetank}{slegetank} \\
  {\bfseries 中文版本：} \zhdigits*{2018}年\zhnumber{12}月 \\
  {\bfseries 中文编译：} \href{https://github.com/redraiment}{张泽鹏} \\
  {\bfseries 编译时间：} \today \\
  \end{minipage}%
}

\vspace{\stretch{2}}

\newpage\thispagestyle{empty}
\begin{quote}\footnotesize
  Copyright \copyright{} 1997 O'Reilly \& Associates, Inc. All rights reserved.
  Printed in the United States of America.

  Nutshell Handbook and the Nutshell Handbook logo are registered trademarks and The Java Series is a trademark of O'Reilly \& Associates, Inc. Many of the designations used by manufacturers and sellers to distinguish their products are claimed as trademarks. Where those designations appear in this book, and O'Reilly \& Associates, Inc. was aware of a trademark claim, the designations have been printed in caps or initial caps.

  While every precaution has been taken in the preparation of this book, the publisher assumes no responsibility for errors or omissions, or for damages resulting from the use of the information contained herein.

  This book is printed on acid-free paper with 85\% recycled content, 15\% post-consumer waste.

  O'Reilly \& Associates is committed to using paper with the highest recycled content available consistent with high quality.

  ISBN: 1-56592-261-1
\end{quote}
